\begin{thebibliography}{69}
  \bibitem{usth} \emph{Mission and Vision}.
    \acrlong{usth}.  Retrieved 2021-07-07.
    \url{https://usth.edu.vn/en/abouts/Mission-et-Vision.html}.
  \bibitem{lake} Huang Fang.
    ``Managing Data Lakes in Big Data Era: What's a data lake
    and why has it became popular in data management ecosystem''.
    \emph{2015 IEEE International Conference on Cyber Technology
    in Automation, Control, and Intelligent Systems}, pp.~820--824.
    IEEE, 2015.  \doi{10.1109/CYBER.2015.7288049}
  \bibitem{micro} Chris Richardson.
    ``1.4.1 Scale cube and microservices''.  \emph{Microservice Patterns}.
    Manning Publications, 2018.  ISBN 9781617294549.
  \bibitem{pure} Brian Göetz, Tim Peierls, Joshua Bloch,
    Joseph Bowbeer and David Holmes.
    ``3.4. Immutability''.  \emph{Java Concurrency in Practice}.
    Addison Wesley Professional, 2006.  ISBN 9780321349606.
  \bibitem{proto} Alan Mark Davis.
    ``Operational Prototyping: A new Development Approach''.
    \emph{IEEE Software}, vol.~9, no.~5, pp.~70--78.
    IEEE, 1992.  \doi{10.1109/52.156899}.
  \bibitem{libredu} Richard Stallman.
    ``Why Schools Should Exclusively Use Free Software''.
    \emph{Free Software and Education}.  GNU Project.  Retrieved 2021-07-14.
    \url{https://www.gnu.org/education/edu-schools.html}.
  \bibitem{qri} \emph{What is Qri?} Qri.io.  Retrieved 2021-07-15.
    \url{https://qri.io/docs/getting-started/what-is-qri}.
  \bibitem{kylo} ``Review Dependencies''.  \emph{Kylo 0.10.0 documentation}.
    Kylo.  Retrieved 2021-07-15.
    \url{https://kylo.rtfd.io/en/v0.10.0/installation/Dependencies.html}
  \bibitem{journal} ``systemd-journal-upload.service(8)''.
    \emph{systemd manual pages}.  Retrieved 2021-07-15.
    \url{https://www.freedesktop.org/software/%
         systemd/man/systemd-journal-upload.service.html}.
  \bibitem{game} Isaac Gouy.
    \emph{Which programming language is fastest?}
    The Computer Language Benchmarks Game.
    Retrieved 2021-07-14.
    \url{https://benchmarksgame-team.pages.debian.net/benchmarksgame}.
  \bibitem{hdfs} \emph{Search Results for HDFS}.
    Packages Search for Linux and Unix.
    Retrieved 2021-07-14.  \url{https://pkgs.org/search/?q=HDFS}.
  \bibitem{crdt} ``Consensus components''.
    \emph{Pinset orchestration for IPFS}.
    Protocol Labs.  Retrieved 2021-07-15.
    \url{https://cluster.ipfs.io/documentation/guides/consensus}.
  \bibitem{ipfs} Juan Benet.
    \emph{IPFS - Content Addressed, Versioned, P2P File System}.
    CoRR, 2014.  \arxiv{1407.3561}.
  \bibitem{exif} Glenn Randers-Pehrson and Tom Lane.
    ``3.7. Exchangeable Image File (Exif) Profile''.
    \emph{Extensions to the PNG 1.2 Specification, Version 1.5.0}.
    Retrieved 2021-07-18.  \url{https://ftp-osl.osuosl.org/pub/%
    libpng/documents/pngext-1.5.0.html#C.eXIf}.
  \bibitem{qricli} \emph{Qri CLI command line reference}.  Qri.io.
    Retrieved 2021-07-18.  \url{https://qri.io/docs/reference/cli_commands}.
  \bibitem{sexpr} John McCarthy.
    ``The LISP Programming System''.
    \emph{Recursive Functions of Symbolic Expressions
    and Their Computation by Machine, Part I}.
    Communications of the ACM, 1960.
\end{thebibliography}
